---
title: "Anova Assignment"
author: "Kai Hendershot"
date: "`r Sys.Date()`"
output: html_document
---
```{r include = FALSE} 
library(readr)
HomeData <- read_csv("C:/Users/kaise/Downloads/HomeData.csv")
library(psych)
library(generics)
library(ggforce)
library(ggformula)
library(car)
library(magrittr)
```
Investigate the hypothesis that the mean price for homes is the same as for 
conditions 3,4 and 5 and for grades 6,7,8 and 9

Make sure condition and grade are factors
```{r}
HomeData$grade <- as.factor(HomeData$grade)
HomeData$condition <- as.factor(HomeData$condition)
```

Create a table to see how balanced the data is 
```{r}
table(HomeData$condition, HomeData$grade)
```

Create a box plot and violin plot for the grade then condition
```{r}
gf_boxplot(price~grade, data = 
             HomeData[HomeData$grade%in% c(6,7,8,9) &
                        HomeData$condition %in% c(3,4,5),], fill = ~condition) %>%
  gf_violin(price~grade, data = 
              HomeData[HomeData$grade%in%c(6,7,8,9) &
                         HomeData$condition%in%c(3,4,5),], fill = ~condition, alpha = .3)%>%
  gf_labs(title = "Overlapping Violin and Box Plot\nfor price, grade, and condition")
```

Create a box plot and violin plot for condition then grade
```{r}
gf_boxplot(price~condition, data = 
             HomeData[HomeData$condition%in%c(3,4,5)&
                        HomeData$grade%in%c(6,7,8,9),], fill = ~grade) %>%
  gf_violin(price~condition, data = 
              HomeData[HomeData$condition%in%c(3,4,5)&
                         HomeData$grade%in%c(6,7,8,9),], fill = ~grade, alpha = .3)%>%
  gf_labs(title = "Overlapping Violin and Box Plot\nfor price, grade, and condition")
```

Use aov on the unbalanced data
```{r}
aov.unb <- aov(price~grade*condition, data = HomeData[HomeData$grade%in%c(6,7,8,9)&
                                             HomeData$condition%in%c(3,4,5),])

summary(aov.unb)
```
After running the test on the unbalanced data we are able to see that all variables
and their comparison p values are of high significance because they are all so small 
they all have some sort of effect on the price of the house.

Initialize storage for new.df
```{r}
new.df <- data.frame(price=integer(), condition=factor(), grade=factor())
```

Create the for loop to create and save the data into new.df
```{r}
for (i in c(6,7,8,9)) {
  for (j in c(3,4,5)) {
    new.df <- rbind(new.df, HomeData[sample(which(HomeData$grade==i &
                                                        HomeData$condition==j),50), c("price", "grade", "condition")])
  }
}
```

Check to see if it worked and how it looks
```{r}
str(new.df)
table(new.df$grade,new.df$condition)
```

Too many zeros so lets focus only on what we need and get rid of those zeros
```{r}
new.df$grade <- droplevels(new.df$grade)
new.df$condition <- droplevels(new.df$condition)
table(new.df$grade, new.df$condition)
```

Run aov test on the new.df as well as Tukey
```{r}
aov.pgc <- aov(price~grade*condition, data = new.df)
summary(aov.pgc)
TukeyHSD(aov.pgc)
```
After running the test on the unbalanced data we are able to see that all variables
and their comparison p values are of high significance because they are all so small 
they all have some sort of effect on the price of the house.

Create a box plot and violin plot for the grade then condition with new.df
```{r}
gf_boxplot(price~grade, data = 
             new.df[new.df$grade%in% c(6,7,8,9) &
                        new.df$condition %in% c(3,4,5),], fill = ~condition) %>%
  gf_violin(price~grade, data = 
              new.df[new.df$grade%in%c(6,7,8,9) &
                         new.df$condition%in%c(3,4,5),], fill = ~condition, alpha = .3)%>%
  gf_labs(title = "Overlapping Violin and Box Plot\nfor price, grade, and condition")
```

Create a box plot and violin plot for condition then grade with new.df
```{r}
gf_boxplot(price~condition, data = 
             new.df[new.df$condition%in%c(3,4,5)&
                        new.df$grade%in%c(6,7,8,9),], fill = ~grade) %>%
  gf_violin(price~condition, data = 
              new.df[new.df$condition%in%c(3,4,5)&
                         new.df$grade%in%c(6,7,8,9),], fill = ~grade, alpha = .3)%>%
  gf_labs(title = "Overlapping Violin and Box Plot\nfor price, grade, and condition")
```


Create a model with car package and using ANOVA
First I had to create a linear model with the variables, then use ANOVA to run 
the test on the model I created, and lastly I printed the results.
```{r}
car_lm <- lm(price~grade*condition, data = HomeData)
anova_car <- anova(car_lm)
print(anova_car)
```
After running the test on the unbalanced data we are able to see that all variables
and their comparison p values are of high significance because they are all so smaller 
they all have some sort of effect on the price of the house.


